A Machine Learning Approach to Kinematic Synthesis of Defect-Free Planar Four-Bar Linkages

### 2018-04-15 idetc2018.tex
Journal version

%%% use twocolumn and 10pt options with the asme2e format
\documentclass[twocolumn,10pt]{asme2e}
\newcommand{\gbf}[1] {\mbox{\boldmath${#1}$\unboldmath}}
\newcommand{\R}{\hbox{I \kern -.5em R}}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{color}
\usepackage{wrapfig}
\usepackage[hidelinks]{hyperref}
\usepackage{subfigure}
\usepackage{url}
\urlstyle{same}
\usepackage{caption}
\usepackage{algorithmicx}
%\usepackage{algorithm}
\usepackage{amsmath}
\usepackage[linesnumbered,ruled]{algorithm2e}

@@

%%% Replace here with information related to your conference
\confshortname{IDETC/CIE 2018}
\conffullname{the ASME 2018 International Design Engineering Technical Conferences \&\\
              Computers and Information in Engineering Conference}

%%%%% for date in a single month, use
\confdate{26-29}
\confmonth{August}
%%%%% for date across two months, use
\confyear{2018}
\confcity{Quebec City}
\confcountry{Canada}

%%% Replace DETC2009/MESA-12345 with the number supplied to you
%%% by ASME for your paper.
\papernum{DRAFT: DETC2018-85578}

@@

\begin{equation}\label{objectiveFunPath}
  \argminA_{\textbf{\emph{l}}, W_i} (1 - Cn_{max}(p, W_i),
\end{equation}
where $\textbf{\emph{l}}$ is the vector of linkage parameters for particular planar linkage, $p$ is signature the of task curve taken as template for Normalized Cross-Correlation and ${\{W_i\}}_{i=0}^{s}$ is the signature set of all $s$ coupler paths generated by the linkage corresponding to $\textbf{\emph{l}}$.
In case of four-bar, $\textbf{\emph{l}}: l_1, l_2, l_3, l_4, l_5$, where $l_i$ is link ratio of $i^{th}$ link shown in Fig~\ref{fourbar}.

@@

\begin{figure}
\begin{tabular}{cc}
  1)\putindeepbox[7pt]{\includegraphics[width=100pt]{figure/path_solutions/path_sol1.eps}}
    & 2)\putindeepbox[7pt]{\includegraphics[width=60pt]{figure/path_solutions/path_sol2.eps}} \\
  3)\putindeepbox[7pt]{\includegraphics[width=120pt]{figure/path_solutions/path_sol3.eps}}
    & 4)\putindeepbox[7pt]{\includegraphics[width=120pt]{figure/path_solutions/path_sol4.eps}}\\
  5)\putindeepbox[7pt]{\includegraphics[width=120pt]{figure/path_solutions/path_sol5.eps}}
    & 6)\putindeepbox[7pt]{\includegraphics[width=120pt]{figure/path_solutions/path_sol6.eps}} \\
  7)\putindeepbox[7pt]{\includegraphics[width=120pt]{figure/path_solutions/path_sol7.eps}}
    & 8)\putindeepbox[7pt]{\includegraphics[width=120pt]{figure/path_solutions/path_sol8.eps}}\\
\end{tabular}
\caption{First eight linkages in the table~\ref{ex1_knnLinkageData} and their resultant coupler paths.}
\label{ex1_solns}
\end{figure}

>>>>

%%% use twocolumn and 10pt options with the asme2e format
\documentclass[twocolumn,10pt]{asme2ej}
\newcommand{\gbf}[1] {\mbox{\boldmath${#1}$\unboldmath}}
\newcommand{\R}{\hbox{I \kern -.5em R}}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{color}
\usepackage{wrapfig}
\usepackage[hidelinks]{hyperref}
\usepackage{subfigure}
\usepackage{url}
\urlstyle{same}
\usepackage{caption}
\usepackage{algorithmicx}
%\usepackage{algorithm}
\usepackage{amsmath}
\usepackage[linesnumbered,ruled]{algorithm2e}

@@

@@

\begin{equation}\label{objectiveFunPath}
  \argminA_{\textbf{\emph{l}}, W_i} (1 - Cn_{max}(p, W_i)),
\end{equation}
where $\textbf{\emph{l}}$ is the vector of linkage parameters for particular planar linkage, $p$ is signature the of task curve taken as template for Normalized Cross-Correlation and ${\{W_i\}}_{i=0}^{s}$ is the signature set of all $s$ coupler paths generated by the linkage corresponding to $\textbf{\emph{l}}$.
In case of four-bar, $\textbf{\emph{l}}: l_1, l_2, l_3, l_4, l_5$, where $l_i$ is link ratio of $i^{th}$ link shown in Fig~\ref{fourbar}.

@@

\begin{figure}
\begin{tabular}{cc}
  1)\putindeepbox[7pt]{\includegraphics[width=100pt]{figure/path_solutions/path_sol1.eps}}
    & 2)\putindeepbox[7pt]{\includegraphics[width=60pt]{figure/path_solutions/path_sol2.eps}} \\
  3)\putindeepbox[7pt]{\includegraphics[width=100pt]{figure/path_solutions/path_sol3.eps}}
    & 4)\putindeepbox[7pt]{\includegraphics[width=100pt]{figure/path_solutions/path_sol4.eps}}\\
  5)\putindeepbox[7pt]{\includegraphics[width=100pt]{figure/path_solutions/path_sol5.eps}}
    & 6)\putindeepbox[7pt]{\includegraphics[width=100pt]{figure/path_solutions/path_sol6.eps}} \\
  7)\putindeepbox[7pt]{\includegraphics[width=100pt]{figure/path_solutions/path_sol7.eps}}
    & 8)\putindeepbox[7pt]{\includegraphics[width=100pt]{figure/path_solutions/path_sol8.eps}}\\
\end{tabular}
\caption{First eight linkages in the table~\ref{ex1_knnLinkageData} and their resultant coupler paths.}
\label{ex1_solns}
\end{figure}
